### 2024-03-29 content/chapter_2.tex
:pencil: Add conclusion

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2023a}.
			One element is in the same group with another if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsubsection}
	\end{subsection}
\end{section}

@@

	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
		Some preference of \gls{wit} and \gls{wpt} are inherently conflicting, for example:
		\begin{itemize}
			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
		\end{itemize}
		Those disparities translate to a fundamental trade-off between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
		\begin{equation}
			\mathcal{C}_\mathrm{R-E}(P) \triangleq \Bigl\{ (r,e) : 0 \le r \le \log(1 + \gamma), \ 0 \le e \le z \Bigr\},
		\end{equation}
		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
	\end{subsection}

@@

	\begin{subsection}{Modulation and Coding Schemes}
		\gls{bc} and \gls{ris} share the same wave scattering model in Section \ref{sc:principles}, but the reflection coefficient $\Gamma$ in \eqref{eq:reflection_coefficient} is exploited in different manners.
		The difference is two-fold:
		\begin{itemize}
			\item \emph{Modulation requires variation:} \gls{bc} relies on dynamically changing the reflection coefficient over time to encode information. This is different from \gls{ris} where the optimal configuration (and reflection coefficient) is fixed for a given channel realization.
			\item \emph{Harvesting requires absorption:} Part of the impinging wave should be fed into the node to power its operation. This is different from \gls{ris} where a full reflection is desired to maximize its channel control capability.
		\end{itemize}
		Denote the amplitude scattering ratio of the \gls{bc} node as $\alpha$, i.e., the power absorption ratio is $(1-\alpha)^2$. Some popular modulation schemes are summarized below:
		\begin{itemize}
			\item \emph{\gls{qam} \cite{Thomas2012a}:} The reflection coefficient corresponding to the $m$-th symbol is
			\begin{equation}
				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert}
			\end{equation}
			where $c_m$ is the corresponding constellation point.
			This scheme is simple but exhibits a low detection \gls{snr} especially when the constellation size is large.
			\item \emph{\gls{fsk} \cite{Abbasi2021a}:} For 2-\gls{fsk}, the reflection coefficient is
			\begin{equation}
				\Gamma(t) =
				\begin{cases}
					\alpha, & t \in \bigl[\frac{n}{\Delta f},\frac{2n+1}{2 \Delta f}\bigr) \\
					-\alpha, & t \in \bigl[\frac{2n+1}{2 \Delta f},\frac{n+1}{\Delta f}\bigr)
				\end{cases}
				= \frac{\pi}{4} \sum_{m=1,\text{odd}}^\infty \frac{\alpha}{m} \sin\bigl(2\pi m \Delta f t\bigr),
			\end{equation}
			where $n \in \mathbb{N}$.
			If the incident wave is a \gls{cw} at frequency $f_0$, the reflected signal is dominated by its first harmonic
			% \begin{equation}
			% 	y(t) = \sum_{m=1,\text{odd}}^\infty \frac{\pi}{4m} \cos(2 \pi f_0 t) \sin\bigl(2\pi m \Delta f t\bigr),
			% \end{equation}
			\begin{equation}
				s_1(t) = \frac{\alpha \pi}{2} \Bigl(\sin\bigl(2 \pi (f_0 {+} \Delta f) t\bigr) - \sin\bigl(2 \pi (f_0 {-} \Delta f) t\bigr)\Bigr).
			\end{equation}
			That is, periodically switching the reflection coefficient at rate $\Delta f$ results in a frequency shift $\pm \Delta f$ on the reflected signal.
			Practical implementations have been demonstrated on a variety of license-free protocols (e.g., HitchHike \cite{Zhang2016a}, Inter-Technology \cite{Iyer2016}, Passive Wi-Fi \cite{Kellogg2017}, \gls{ble}-Backscatter \cite{Ensworth2017}) where the mirror copy can be suppressed.
			\item \emph{\gls{css} \cite{Talla2017}:} A chirp is a signal whose frequency increases or decreases over time.
			\gls{css} uses wideband linear-frequency modulated chirps to encode information, which is from \gls{dsss} and \gls{fsss} with pseudo-random sequences and \gls{fsk} with discrete frequencies.
			In particular, $N+1$ reflection coefficients of the same envelope are sequentially selected at a regular rate $\Delta f$, given by
			\begin{equation}
				\Gamma_n = \alpha \exp(\jmath \phi_n), \quad n \in \{0, 1, \ldots, N\},
			\end{equation}
			where $\phi_n = \frac{2 \pi}{\Delta f}(A n^2 + B n)$ and $A$, $B$ are constants.
			As the core modulation scheme in \gls{lora}, it is more robust to noise and interference (with a reception sensitivity of -149 dBm), harder to be detected by eavesdroppers, and can be used for ranging and localization \cite{Abbasi2021a}.

>>>>

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2024}.
			One element is in the same group with another if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsubsection}
	\end{subsection}
\end{section}

@@

	\begin{subsection}{\glsfmtfull{r-e} Trade-off}
		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
		Some preference of \gls{wit} and \gls{wpt} are inherently conflicting, for example:
		\begin{itemize}
			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
		\end{itemize}
		Those disparities translate to a fundamental trade-off between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
		\begin{equation}
			\mathcal{C}_\mathrm{R-E}(P) \triangleq \Bigl\{ (r,e) : 0 \le r \le \log(1 + \gamma), \ 0 \le e \le z \Bigr\},
		\end{equation}
		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
	\end{subsection}

@@

	\begin{subsection}{Modulation and Coding Schemes}
		\gls{bc} and \gls{ris} share the same wave scattering model in Section \ref{sc:principles}, but the reflection coefficient $\Gamma$ in \eqref{eq:reflection_coefficient} is exploited in different manners.
		The difference is two-fold:
		\begin{itemize}
			\item \emph{Modulation requires variation:} \gls{bc} relies on dynamically changing the reflection coefficient over time to encode information. This is different from \gls{ris} where the optimal configuration (and reflection coefficient) is fixed for a given channel realization.
			\item \emph{Harvesting requires absorption:} Part of the impinging wave should be fed into the node to power its operation. This is different from \gls{ris} where a full reflection is desired to maximize its channel control capability.
		\end{itemize}
		Denote the amplitude scattering ratio of the \gls{bc} node as $\alpha$, i.e., the power absorption ratio is $(1-\alpha)^2$. Some popular modulation schemes are summarized below:
		\begin{itemize}
			\item \emph{\gls{qam} \cite{Thomas2012a}:} The reflection coefficient corresponding to the $m$-th symbol is
			\begin{equation}
				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert}
			\end{equation}
			where $c_m$ is the corresponding constellation point.
			This scheme is simple but exhibits a low detection \gls{snr} especially when the constellation size is large.
			\item \emph{\gls{fsk} \cite{Abbasi2021a}:} For 2-\gls{fsk}, the reflection coefficient is
			\begin{equation}
				\Gamma(t) =
				\begin{cases}
					\alpha, & t \in \bigl[\frac{n}{\Delta f},\frac{2n+1}{2 \Delta f}\bigr) \\
					-\alpha, & t \in \bigl[\frac{2n+1}{2 \Delta f},\frac{n+1}{\Delta f}\bigr)
				\end{cases}
				= \frac{\pi}{4} \sum_{m=1,\text{odd}}^\infty \frac{\alpha}{m} \sin\bigl(2\pi m \Delta f t\bigr),
			\end{equation}
			where $n \in \mathbb{N}$.
			If the incident wave is a \gls{cw} at frequency $f_0$, the reflected signal is dominated by its first harmonic
			% \begin{equation}
			% 	y(t) = \sum_{m=1,\text{odd}}^\infty \frac{\pi}{4m} \cos(2 \pi f_0 t) \sin\bigl(2\pi m \Delta f t\bigr),
			% \end{equation}
			\begin{equation}
				s_1(t) = \frac{\alpha \pi}{2} \Bigl(\sin\bigl(2 \pi (f_0 {+} \Delta f) t\bigr) - \sin\bigl(2 \pi (f_0 {-} \Delta f) t\bigr)\Bigr).
			\end{equation}
			That is, periodically switching the reflection coefficient at rate $\Delta f$ results in a frequency shift $\pm \Delta f$ on the reflected signal.
			Practical implementations have been demonstrated on a variety of license-free protocols (e.g., HitchHike \cite{Zhang2016a}, inter-technology \cite{Iyer2016}, Passive Wi-Fi \cite{Kellogg2017}, \gls{ble}-Backscatter \cite{Ensworth2017}) where the mirror copy can be suppressed.
			\item \emph{\gls{css} \cite{Talla2017}:} A chirp is a signal whose frequency increases or decreases over time.
			\gls{css} uses wideband linear-frequency modulated chirps to encode information, which is from \gls{dsss} and \gls{fsss} with pseudo-random sequences and \gls{fsk} with discrete frequencies.
			In particular, $N+1$ reflection coefficients of the same envelope are sequentially selected at a regular rate $\Delta f$, given by
			\begin{equation}
				\Gamma_n = \alpha \exp(\jmath \phi_n), \quad n \in \{0, 1, \ldots, N\},
			\end{equation}
			where $\phi_n = \frac{2 \pi}{\Delta f}(A n^2 + B n)$ and $A$, $B$ are constants.
			As the core modulation scheme in \gls{lora}, it is more robust to noise and interference (with a reception sensitivity of -149 dBm), harder to be detected by eavesdroppers, and can be used for ranging and localization \cite{Abbasi2021a}.

### 2024-03-29 content/chapter_4.tex
:pencil: Add conclusion

	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
\end{section}

>>>>

	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2024} and learning-based approaches can be promising.
	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
\end{section}

### 2024-03-29 content/chapter_5.tex
:pencil: Add conclusion

	The answer depends heavily on the hardware architecture and scattering model.
	In diagonal \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which physically connects adjacent elements using passive components.
	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries \eqref{eq:diagonal_scattering_matrix} to block diagonal with unitary blocks \eqref{eq:bd_scattering_matrix}.
	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.

@@

\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
	The overall scattering matrix of the \gls{bd}-\gls{ris} is
	\begin{equation}
		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
	\end{equation}
	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
	That is, $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.

>>>>

	The answer depends heavily on the hardware architecture and scattering model.
	In diagonal \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which physically connects adjacent elements using passive components.
	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries \eqref{eq:diagonal_scattering_matrix} to block diagonal with unitary blocks \eqref{eq:bd_scattering_matrix}.
	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2024}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2024,Li2023d,Bartoli2023,Li2023c}.
	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.

@@

\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2024,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
	The overall scattering matrix of the \gls{bd}-\gls{ris} is
	\begin{equation}
		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
	\end{equation}
	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
	That is, $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2024}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
